Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-24 man/figures/plot_spei12.Rmd
fix errors

```{r plot_spei}
plot_spei <- spei %>%   
  ggplot(aes(x=date, y=spei, fill = sign)) + 
  geom_bar(stat = "identity") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "brown4")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = '', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12))

@@

**Appendix S2**. Drought severity in the Sierra Nevada for the 1950-2016 period based on the Standardised Precipitation-Evapotranspiration Index (SPEI). Data from Global SPEI database (http://spei.csic.es/database.html). We obtanied the SPEI data for a 12 month scale and for all 0.5º grid cells covering Sierra Nevada.

>>>>

```{r plot_spei}
plot_spei <- spei %>%   
  ggplot(aes(x=date, y=spei, fill = sign)) + 
  geom_bar(stat = "identity", colour = "transparent") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "brown4")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = 'Year', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12))

@@

**Figure S2**. Drought severity in the Sierra Nevada for the 1950-2016 period based on the Standardised Precipitation-Evapotranspiration Index (SPEI). Data from Global SPEI database (http://spei.csic.es/database.html). We obtanied the SPEI data for a 12 month scale and for all 0.5º grid cells covering Sierra Nevada.

### 2018-11-24 man/figures/ring_climate.Rmd
update figures
fix errors

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 6), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5)),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
) 
```

@@

```{r plot_out, fig.height=7, dpi = 300, out.width = 0.8} 
ring_climate
```

>>>>

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 6), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 7),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 7),
        axis.text.y = element_text(size = 7), 
        axis.title.y = element_text(size = 8),
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm")),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
) 
```

@@

```{r plot_out, fig.height=6, dpi = 300, out.width = 0.8} 
ring_climate
```
